\section{Master Control}

\paragraph{}
The main code for the quadrotor can be found in the {\it master.c} file.  The program first sets up serial communication and the various devices to be used by the AVR ($I^2C$, ADC, and motors) in addition to the takeoff controller.  It then enters into the main control loop where it continuously polls three different flags.  

\paragraph{}
The first flag, {\bf serial_command_ready}, indicates that a serial command has been received and thus should be handled.  In this case, {\bf forward_command()} is called which processes takes any action necessary to fulfill the command.

\paragraph{}
The second flag, {\bf TOP\_flag}, causes the AVR to poll the sonar device attached to the slave AVR chip and send flight data back to the PC via the {\bf send_spam()} function.  If the quadrotor is currently in takeoff or landing mode, this interrupt is also where the base thrust of the motors is changed accordingly.

\paragraph{}
The final flag, {\bf compare\_A\_flag}, prompts the AVR to poll the gyroscope, magnetometer, accelerometer, and gyroscope in that order.  The gyroscope is polled twice to get data for both the x and y rotational axes.  When this is done, the roll and pitch are filtered as previously described and the motor values are updated via the {\bf update\_motors()} function call.

\paragraph{}
A pseudocode representation of the main code follows:

{\bf
\tab begin:
\tab \tab setup serial
\tab \tab setup devices
\tab \tab loop forever:
\tab \tab \tab if serial command is ready:
\tab \tab \tab \tab handle command
\tab \tab \tab if 30 Hz flag is set:
\tab \tab \tab \tab poll sonar
\tab \tab \tab \tab filter and update altitude
\tab \tab \tab \tab send flight info to PC
\tab \tab \tab if 122 Hz flag is set:
\tab \tab \tab \tab poll gyroscope
\tab \tab \tab \tab poll magnetometer
\tab \tab \tab \tab poll accelerometer
\tab \tab \tab \tab poll gyroscope
\tab \tab \tab \tab filter and update roll and pitch
\tab \tab \tab \tab if quadrotor is flying:
\tab \tab \tab \tab \tab update motors
\tab \tab end loop
\tab end

